Git Learning Notes

### 2014-09-28 ch-intro/ch-intro.tex
SI info inserted into main text

Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then electron-hole pairs generate free radicals, i.e., \ce{OH.}, which enable further reactions. For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
\begin{subequations}\label{eq:h2o}
\begin{align}
4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
\end{align}
\end{subequations}
As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2} versus \gls{nhe}, and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}. So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone. Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
% wo3 vs NHE
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{woxnhe.jpg}
\caption[Bands positions of \ce{WO3} versus NHE]{Bands positions of \ce{WO3} in contact with aqueous electolyte at pH 1, adapted from Ref.\cite{Gratzel2001}}
\label{fig:woxnhe}
\end{figure}
Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}. The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}

>>>>

Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then electron-hole pairs generate free radicals, i.e., \ce{OH.}, which enable further reactions. For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
\begin{subequations}\label{eq:h2o}
\begin{align}
4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
\end{align}
\end{subequations}
As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2} versus \gls{nhe}, and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}. So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone. Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
% wo3 vs NHE
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{woxnhe.jpg}
\caption[Bands positions of \ce{WO3} versus NHE]{Bands positions of \ce{WO3} in contact with aqueous electolyte at pH 1, adapted from Ref.\cite{Gratzel2001}}
\label{fig:woxnhe}
\end{figure}
Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}. The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}

For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals to the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH=0.\cite{Osterloh2008} Flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.

### 2014-09-28 ch-tms/tmspart.tex
SI info inserted into main text

\subsection{Synthesis Review of TMDCs}
Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e., \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well. \citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Hence this study just recapitulates the main categories of synthesis methods:
\begin{enumerate}
\item Reducing \ce{MO3} in \ce{H2} and \ce{H2S} atmosphere;\footnote{M = Mo, W in this work}
\item Direct decomposition of \ce{MS3};
\item Decomposition of the ammonium salt \ce{(NH4)2MS4};
\item Using CNT as templates, arc discharge, or laser ablation.
\end{enumerate}
Except the aforementioned methods, another important reaction in CVD domain is
\begin{equation}\label{eq:mclns}
\cee{MoCl5(WCl6) + S \rightarrow MoS2(WS2) + S2Cl2}.
\end{equation}
This reaction has been explored by several authors\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}

>>>>

The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} 
The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \AA. This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube. The diameter of a nanotube is given by 
\begin{equation}
d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}
\end{equation}
Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the cosine times 2 is unit. 
In analog with carbon nanotube, chiral angle $\theta$ is given by
\begin{equation}
\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}
\end{equation}

Chiral angles from the interval $[0,pi/6]$ is sufficient for all possible tubes. Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,pi/6)$. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_tube1}
\caption[\ce{WS2} nanotube rolling]{\ce{WS2} nanotube rolling}
\label{fig:ch5ntroll}
\end{figure}

\subsection{Synthesis Review of TMDCs}
Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e., \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well. \citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Hence this study just recapitulates the main categories of synthesis methods:
\begin{enumerate}
\item Reducing \ce{MO3} in \ce{H2} and \ce{H2S} atmosphere;\footnote{M = Mo, W in this work}
\item Direct decomposition of \ce{MS3};
\item Decomposition of the ammonium salt \ce{(NH4)2MS4};
\item Using CNT as templates, arc discharge, or laser ablation.
\end{enumerate}
Except the aforementioned methods, another important reaction in CVD domain is
\begin{equation}\label{eq:mclns}
\cee{MoCl5(WCl6) + S \rightarrow MoS2(WS2) + S2Cl2}.
\end{equation}
\begin{align}
\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
\end{align}
This reaction has been explored by several authors\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}

### 2014-09-28 ch-wox/part1.tex
SI info inserted into main text

In the past decades, tons of works have been devoted to understanding the chromogenic phenomena in \ce{WO3}. Several key results were highlighted as reviewed in Ref.\cite{Deb2008},
\begin{itemize}
    \item coloration and bleaching can also be stimulated by other routes, such as by UV irradiation, thermal treating, heating in vacuum, reducing atmosphere, \emph{etc}
    \item no electrical coloration occurs in vacuum, but other routes still work
    \item coloration is associated with a proportional increase in conductivity
    \item coloration spectrum is essentially similar in all cases except small variation in peak position
    \item coloration is structural sensitive and most efficient in amorphous films
\end{itemize}

@@

>>>>

In the past decades, tons of works have been devoted to understanding the chromogenic phenomena in \ce{WO3}. Several key results were highlighted as reviewed in Ref.\cite{Deb2008}:
\begin{itemize}
    \item coloration and bleaching can also be stimulated by other routes, such as by UV irradiation, thermal treating, heating in vacuum, reducing atmosphere, \emph{etc};
    \item no electrical coloration occurs in vacuum, but other routes still work;
    \item coloration is associated with a proportional increase in conductivity;
    \item coloration spectrum is essentially similar in all cases except small variation in peak position;
    \item coloration is structural sensitive and most efficient in amorphous films.
\end{itemize}

@@

\ce{WO3} and optical electric field enhancement. The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure. Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every n row. Actually the value x in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3. \ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure. Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$. For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where x is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for x within 2.87 to 2.93.\cite{Sloan1999} The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm \ce{WO3}. Localized surface plasmons could possibly exist on these conductive planes. Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.   \citeauthor{Shingaya2013} also synthesized \ce{WS2}-\ce{WO_x} core-shell structures and found similar Raman scattering enhancement. The x value is estimated by the Raman spectra peaks.\cite{Shingaya2013}(Data not shown in patent)

### 2014-09-28 figure_table.tex
ch2 enhanced
wox and moox proofreading
SI info inserted into main text

@@

@@

\begin{figure}[htb]
\centering
\subcaptionbox{\label{fig:moind}}{\includegraphics{n_MoO3}}%
\subcaptionbox{\label{fig:mocon}}{\includegraphics{Graph20}}
\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis. (b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si. The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
\label{fig:mofl}
\end{figure}

@@

\subsection{chromic}

the electrical conductivity is given by $\sigma = n e \mu$, where $n$ is the density of free carriers, $\mu$ is their mobility and $e$ is electronic charge. The mobility is given by $\mu = e\tau/m^*$ with $\tau$ is carrier resistivity relaxation time and $m^*$ is the carrier effective mass.

The degree of \ce{H^+} intercalation, $x$, is determined by integrating cathodic current, and given by
\begin{equation}
x = \frac{Q}{F}\frac{M_\ce{WO3}}{m_f}
\end{equation}
where $m_f$ is the mass of film, $M_\ce{WO3}$ is the molar mass of \ce{WO3*1/3H2O}, and F is Faraday's constant.
The color center density, $c$, is then obtained using formula
\begin{equation}
c= \frac{x M_\ce{WO3}N_A}{\rho}
\end{equation}
where $N_A$ is Avogadro number, $\rho$ is density of film.

In second state, the one with smaller droplet probably would exhibit faster growth rate in $\langle001\rangle$ direction due to its shortest lattice constant, while the other one endures more growth along$\langle010\rangle$ direction. We suspect that the liquid size that induce the tower growth is much larger than that of belts. From the final morphology of as-synthesized sample, we find that the above proposed two growth approaches could change into each other, that is belt growth could be initiated on the top of tower growth and vice visa. We assume this phenomena arise from the interaction between vapor supply, temperature and the shape of liquid catalyst. Or it may just come from the vapor transport of \ce{NaxMoO3}.
It had been shown by actively engineering the shape of catalysis, the growth direction of  InP NW could be switched between [111] and [100].\cite{Wang2013c} The same mechanism might exist in our case as well. For instance, when a belt is sufficient long and it could extend into the low temperature part, where the supply of MoOx vapor is reduced due to the consumption, and the shape of liquid might vary as well. Both will result in different absorption and subsequent diffusion rate along and inside the liquid catalyst. We also observed that belt growth could initiate from tower growth in reduced time growth. Actually this may be one possible mechanism of belts formation.

(The presence of \ce{Na6MoO33} phase is an indirect evidence for the formation of eutectic \ce{Na2MoO4}- \ce{MoO3} binary compounds at growth temperature. The bulk phase diagram may not accurately represent the phase transition occurring in catalyst droplet and solid interface. And it will usually lead to a significant temperature decrease of eutectic point from the bulk value. Nanoparticles do not completely melt and instead act as an active site for reactant absorption and diffusion, leading to a vapor-solid-solid growth mechanism. )

>>>>

\subsection{misc}

@@

\si{\angstrom}

Inline lists, which are sequential in nature, just like enumerated lists, but are
\begin{enumerate*}[label=\itshape\alph*\upshape)]
\item formatted within their paragraph;
\item usually labelled with letters; and
\item usually have the final item prefixed with `and' or `or',
\end{enumerate*} like this example.

@@

%float package
\begin{figure}[htb]
\centering
\subcaptionbox{\label{fig:moind}}{\includegraphics{n_MoO3}}%
\subcaptionbox{\label{fig:mocon}}{\includegraphics{Graph20}}
\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis. (b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si. The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
\label{fig:mofl}
\end{figure}

@@

\section{vocabulary}
well suited to,
seriously pursued. 
One must be just as aware of the instrument's limitations as one is of its advantages
I call attention to the fact that.
arise as a result of, dispersal of Na by electron probe.
$\delta\omega/\epsilon$

\subsection{pronunciation}

chamber, vias, valve, figure, energetic, managerial, inert, volatile, chromic,
laminar, palladium, platinum, photovoltaic, acronym, chirality, stoichiometric, cyclic voltammetry, quasi, pseudo,
